### 2021-06-21 publications/2020-03-paper/revisions/review-responses.tex

        %--------------------------------------------------------------------
                        \question In a country such as Japan, which has been badly impacted by nuclear disasters, how can nuclear power be part of the suggested energy mix for carbon neutral future? Line no. 18-19 in P-2 directly contradicts line no 34-36 in the abstract page.

        \begin{solution}

                 Thank you for your comment. We have touched upon this issue in our discussion, by identifying a need for improving safety standards within the Japanese regulatory framework, and for the need of engendering public acceptance by creating trust in nuclear power. To further emphasise the urgency of using existing options like nuclear power, the following sentence has been added to the discussion section in light of recent developments

                 \begin{itemize}
                 \item An approach reliant on a mature technology like nuclear also improves the likelihood of Japan meeting its 2050 emission goals, as the timely success of the Japanese hydrogen plan is far from certain especially considering the more ambitious carbon reduction goals recently announced by METI[42, 43].
                 \end{itemize}

### 2021-06-21 publications/2020-03-paper/changes/acks.tex
Adds 'track changes' copy

\section{CRediT Statement}

The authors contributed to this work as described below.

\textbf{Anshuman Chaube}: Methodology, validation, writing - original draft, visualisation.

\textbf{Andrew Chapman}: Methodology, validation,  writing - original draft, writing - review and editing.

\textbf{Akari Minami}: data curation, validation.

\textbf{James Stubbins}: writing - review and editing, supervision.

\textbf{Kathryn D. Huff}: Conceptualisation, resources, writing - review and editing, supervision.

>>>>

%\section{CRediT Statement}
%
%The authors contributed to this work as described below.
%
%\textbf{Anshuman Chaube}: Methodology, validation, writing - original draft, visualisation.
%
%\textbf{Andrew Chapman}: Methodology, validation,  writing - original draft, writing - review and editing.
%
%\textbf{Akari Minami}: data curation, validation.
%
%\textbf{James Stubbins}: writing - review and editing, supervision. 
%
%\textbf{Kathryn D. Huff}: Conceptualisation, resources, writing - review and editing, supervision.

### 2021-06-21 publications/2020-03-paper/changes/conclusion-revised.tex
Adds 'track changes' copy

Mitigating emissions from the industrial and transportation sector presents unique challenges that may affect the amount of emission reduction required from the electricity supply sector to meet Japan's 2030 and 2050 goals. Future work should incorporate holistic assessment of the entire Japanese energy system when exploring energy transition pathways. The assessment of synergistic utilisation of hydrogen in transportation and industry alongside electricity storage and supply is vital for policy decisions. The effect of transportation media such as trucks and pipelines on hydrogen and CCS is also worth investigating. Any new technologies that develop in the future and promise rapid decarbonisation should also be incorporated in such work. Finally, economic feasibility analyses with respect to national budget requirements and projected GDP trends must also be conducted to improve decarbonisation strategies, improve social outcomes, and delineate investment goals for the energy sector.

>>>>

Mitigating emissions from the industrial and transportation sector presents unique challenges that may affect the amount of emission reduction required from the electricity supply sector to meet Japan's 2030 and 2050 goals. Future work should incorporate holistic assessment of the entire Japanese energy system when exploring energy transition pathways. The assessment of synergistic utilisation of hydrogen in transportation and industry alongside electricity storage and supply is vital for policy decisions. The effect of transportation media such as trucks and pipelines on hydrogen and CCS is also worth investigating. \added{Any new technologies that develop in the future and promise rapid decarbonisation should also be incorporated in such work.} Finally, economic feasibility analyses with respect to national budget requirements and projected GDP trends must also be conducted to improve decarbonisation strategies, improve social outcomes, and delineate investment goals for the energy sector.

### 2021-06-21 publications/2020-03-paper/changes/introduction-revised.tex
Adds 'track changes' copy

\section{Introduction} \label{Introduction}
In order to mitigate climate change and to improve environmental outcomes, many nations are actively seeking to reduce carbon emissions, and have formalised this goal through the Paris Agreements \cite{united_nations_framework_convention_on_climate_change_unfccc_submission_2015}. The largest contribution to global \gls{GHG} emissions, some 73\%, comes from energy consumption in the transportation, electricity and heat, buildings, manufacturing, and construction sectors \cite{ge_4_2020}. Energy use in buildings in particular generates 17.5\% of all emissions \cite{ritchie_emissions_2021}. However, there is significant uncertainty surrounding these carbon-neutral energy transitions regarding the economically optimal shares and deployment rates of clean energy sources and their long-term impact on the energy system. The emergence of novel technologies like high-efficiency utility-scale \gls{CCS} (henceforth referred to as \gls{CCS}) and hydrogen power also raises questions about their role in \gls{GHG} mitigation and the sensitivity of the energy transition to uncertainties in these technologies' investment cost, efficiency, and carbon footprint.

We are probing these questions by simulating cost-optimised energy transitions in the electricity supply sector with rigid carbon constraints using a suite of existing and emerging electricity generation and storage technologies. We use Japan as a proxy for a developed nation committed to addressing climate change. However, the results have global significance. Like many other developed nations, Japan has been rapidly deploying renewables, and in the wake of the Fukushima Daiichi accident, it shut down its nuclear reactors and increased its reliance on coal \cite{international_energy_agency_latest_2019, noauthor_electricity_2019}. However, now Japan is reinvigorating its nuclear power sector, as evidenced by the restart of some of its nuclear reactors \cite{iaea_pris_nodate}. Additionally, Japan is actively developing plans to deploy hydrogen power under the Basic Hydrogen Strategy \cite{noauthor_basic_2017} and has shown interest in utilising \gls{CCS} \cite{meti_report_2020}. Therefore, due to Japan's similarity to other developed nations and its willingness to consider a variety of commercial and pre-commercial low-carbon technologies, simulating likely transition pathways for decarbonisation of the Japanese electricity sector could inform global energy policy. Our simulations provide these insights by delineating potential transition scenarios that consider multiple combinations of a variety of technological options, and our sensitivity analyses identify key novel technologies and their most significant parameters.

%Developed nations rich in natural resources can reduce \gls{GHG} emissions by switching to natural gas or implementing \gls{CCS} at fossil fuel plants. However, these options are often economically infeasible for developing nations, which will lead to increased emissions through greater coal use \cite{international_energy_agency_latest_2019}. Japan, a developed nation without fossil fuel resources, is likely to follow a different path to reduce emissions, evidenced by the restart of nuclear reactors and a shift towards large-scale renewable energy deployment .

>>>>

\section{Introduction} \label{Introduction}
In order to mitigate climate change and to improve environmental outcomes, many nations are actively seeking to reduce carbon emissions, and have formalised this goal through the Paris Agreements \cite{united_nations_framework_convention_on_climate_change_unfccc_submission_2015}. The largest contribution to global \gls{GHG} emissions, some 73\%, comes from energy consumption in the transportation, electricity and heat, buildings, manufacturing, and construction sectors \cite{ge_4_2020}. \added{Energy use in buildings in particular generates 17.5\% of all emissions \mbox{
\cite{ritchie_emissions_2021}}.} However, there is significant uncertainty surrounding these carbon-neutral energy transitions regarding the economically optimal shares and deployment rates of clean energy sources and their long-term impact on the energy system. The emergence of novel technologies like \added{high-efficiency utility-scale }  \gls{CCS} \added{(henceforth referred to as }\gls{CCS}\added{) }  and hydrogen power also raises questions about their role in \gls{GHG} mitigation and the sensitivity of the energy transition to uncertainties in these technologies' investment cost, efficiency, and carbon footprint.

We are probing these questions by simulating cost-optimised energy transitions in the electricity supply sector with rigid carbon constraints using a suite of existing and emerging electricity generation and storage technologies. We use Japan as a proxy for a developed nation committed to addressing climate change. However, the results have global significance. Like many other developed nations, Japan has been rapidly deploying renewables \deleted{and has attempted to transition away from nuclear power since the }  \added{, and in the wake of the }  Fukushima Daiichi accident \deleted{\mbox{
\cite{international_energy_agency_latest_2019}}. Yet Japan is also considering }  \added{, it shut down its nuclear reactors and increased its reliance on coal \mbox{\cite{international_energy_agency_latest_2019, noauthor_electricity_2019}}. However, now Japan is } reinvigorating its nuclear power sector, \added{as} evidenced by the restart of \added{some of} its nuclear reactors \cite{iaea_pris_nodate}. Additionally, Japan is actively developing plans to deploy hydrogen power under the Basic Hydrogen Strategy \cite{noauthor_basic_2017} and has shown interest in utilising \gls{CCS} \cite{meti_report_2020}. Therefore, due to Japan's similarity to other developed nations and its willingness to consider a variety of commercial and pre-commercial low-carbon technologies,  \deleted{lessons learnt from these decarbonisation simulations} \added{simulating likely transition pathways for decarbonisation of the Japanese electricity sector} could inform global energy policy \added{. Our simulations provide these insights} by delineating potential transition \deleted{pathways, identifying} \added{scenarios that consider multiple combinations of a variety of technological options, and our sensitivity analyses identify} key novel technologies  \deleted{,} and their most significant parameters.
%
%%Developed nations rich in natural resources can reduce \gls{GHG} emissions by switching to natural gas or implementing \gls{CCS} at fossil fuel plants. However, these options are often economically infeasible for developing nations, which will lead to increased emissions through greater coal use \cite{international_energy_agency_latest_2019}. Japan, a developed nation without fossil fuel resources, is likely to follow a different path to reduce emissions, evidenced by the restart of nuclear reactors and a shift towards large-scale renewable energy deployment .

### 2021-06-21 publications/2020-03-paper/changes/litreview-revised.tex
Adds 'track changes' copy

Taking a more holistic view in line with the Japanese government's 3E+S targets, ambitious research and development to enable high levels of renewable deployment is necessary to not only meet deep emission reduction goals, but to also reduce Japanese dependence on imported fuels, which would affect both CCS and nuclear deployment rates into the future. Consensus on policy options and priorities also has a large influence on modelling outcomes for the Low Carbon Navigator, which assesses Japanese energy and emission options out to 2050 \cite{moinuddin_japan_2019}. A seminal work by Sugiyama et al. harmonises a number of modelling approaches for Japan's long-term (up to 2050) climate change mitigation options, utilising national and global general and partial equilibrium models \cite{sugiyama_japans_2019}. Model results are contrasted under six scenarios which incorporate a baseline, a range of emissions reductions (50-80\%), and regional obligations for global models (ibid.) under the Paris Agreement target of an 80\% reduction. Each of the models assessed recognise the importance of renewable energy deployment by 2050, notably hydro, solar, and wind, with varying contributions from nuclear energy and fossil fuels, predominantly natural gas. Additionally, for Japan, the option of importing carbon-free hydrogen was identified as potentially playing a critical role \cite{akimoto_estimates_2010, matsuo_global_2013, oshiro_diffusion_2015, sugiyama_japans_2019}. Many studies consider hydrogen a critical part of Japan's low-carbon energy transition, as it can improve energy security, it can be produced from multiple sources, and lacks emissions from fuel combustion \cite{iida_hydrogen_2019}. Global modelling efforts consider the incorporation of long-distance international transport of hydrogen with end uses dominated by passenger and freight fuel cell vehicles and power generation, via both mixed and direct combustion. Electricity from hydrogen is estimated to emerge in Japan from 2030 onwards, as nuclear and coal-fired power generation reduce towards 2050 \cite{ishimoto_significance_2017}. From a policy standpoint, Japan has committed to achieving a hydrogen society, with the primary goal of cost parity of hydrogen with competing fuels, which requires a three-fold reduction in cost by 2030 and further reductions into the future \cite{nagashima_japans_2018}. Under the Basic Hydrogen Strategy, the Japanese government aims to realise low cost hydrogen use in power generation, mobility, and industry, develop international supply chains to ensure stable supply, expand renewable deployment, revitalise regional areas, and develop hydrogen related technologies \cite{meti_basic_2017}. The strategy aims to account for both economic and geopolitical impacts and the need to prioritise research and development to overcome the economic and technical challenges \cite{nagashima_japans_2018}. A common thread across previous research is the uncertainty surrounding \gls{CCS}, particularly with regard to scaling up and public acceptance issues, and the role that nuclear energy will play, largely due to policy reform which occurred after the Fukushima nuclear accident \cite{oshiro_mid-century_2019}.

The model and the approach proposed in this research uniquely build on the modelling consensus outlined in the literature review and expand the consideration of technologies by including emerging near-term alternatives, and potentially disruptive technologies post-2050. This work leverages the dynamic simulation capabilities of \gls{TIMES} \cite{loulou_etsap-tiam_2008} by incorporating learning curves for parameters such as investment and \gls{OM} costs, efficiency, and emission coefficients. Our model incorporates not only direct emissions, but also lifecycle emissions of all conventional and emerging technologies, the latter of which is an often neglected externality. This enables a more meaningful analysis of the global warming potential of emerging technologies, as life-cycle emissions become significant when considering deep emission reductions of the order of 80\% from current levels. By modelling the Japanese electricity supply system out to the year 2100, our aim is to detail the mid- to long-term impacts of technological development and market penetration, and to identify the suite of technologies which could underpin the successful achievement of carbon reduction.

>>>>

Taking a more holistic view in line with the Japanese government's 3E+S targets, ambitious research and development to enable high levels of renewable deployment is necessary to not only meet deep emission reduction goals, but to also reduce Japanese dependence on imported fuels, which would affect both CCS and nuclear deployment rates into the future. Consensus on policy options and priorities also has a large influence on modelling outcomes for the Low Carbon Navigator, which assesses Japanese energy and emission options out to 2050 \cite{moinuddin_japan_2019}. A seminal work by Sugiyama et al. harmonises a number of modelling approaches for Japan's long-term (up to 2050) climate change mitigation options, utilising national and global general and partial equilibrium models \cite{sugiyama_japans_2019}. Model results are contrasted under six scenarios which incorporate a baseline, a range of emissions reductions (50-80\%), and regional obligations for global models (ibid.) under the Paris Agreement target of an 80\% reduction. Each of the models assessed recognise the importance of renewable energy deployment by 2050, notably hydro, solar, and wind, with varying contributions from nuclear energy and fossil fuels, predominantly natural gas. Additionally, for Japan, the option of importing carbon-free hydrogen was identified as potentially playing a critical role \cite{akimoto_estimates_2010, matsuo_global_2013, oshiro_diffusion_2015, sugiyama_japans_2019}. Many studies consider hydrogen a critical part of Japan's low-carbon energy transition, as it can improve energy security, it can be produced from multiple sources, and lacks emissions from fuel combustion \cite{iida_hydrogen_2019}. Global modelling efforts consider the incorporation of long-distance international transport of hydrogen with end uses dominated by passenger and freight fuel cell vehicles and power generation, via both mixed and direct combustion. Electricity from hydrogen is estimated to emerge in Japan from 2030 onwards, as nuclear and coal-fired power generation reduce towards 2050 \cite{ishimoto_significance_2017}. From a policy standpoint, Japan has committed to achieving a hydrogen society, with the primary goal of cost parity of hydrogen with competing fuels, which requires a three-fold reduction in cost by 2030 and further reductions into the future \cite{nagashima_japans_2018}. Under the Basic Hydrogen Strategy, the Japanese government aims to realise low cost hydrogen use in power generation, mobility, and industry, develop international supply chains to ensure stable supply, expand renewable deployment, revitalise regional areas, and develop hydrogen related technologies \cite{noauthor_basic_2017}. The strategy aims to account for both economic and geopolitical impacts and the need to prioritise research and development to overcome the economic and technical challenges \cite{nagashima_japans_2018}. A common thread across previous research is the uncertainty surrounding \gls{CCS}, particularly with regard to scaling up and public acceptance issues, and the role that nuclear energy will play, largely due to policy reform which occurred after the Fukushima nuclear accident \cite{oshiro_mid-century_2019}.

The model and the approach proposed in this research uniquely build on the modelling consensus outlined in the literature review and expand the consideration of technologies by including emerging near-term alternatives, and potentially disruptive technologies post-2050. This work leverages the dynamic simulation capabilities of \gls{TIMES} \cite{loulou_etsap-tiam:_2008} by incorporating learning curves for parameters such as investment and \gls{OM} costs, efficiency, and emission coefficients. Our model incorporates not only direct emissions, but also lifecycle emissions of all conventional and emerging technologies, the latter of which is an often neglected externality. This enables a more meaningful analysis of the global warming potential of emerging technologies, as life-cycle emissions become significant when considering deep emission reductions of the order of 80\% from current levels. By modelling the Japanese electricity supply system out to the year 2100, our aim is to detail the mid- to long-term impacts of technological development and market penetration, and to identify the suite of technologies which could underpin the successful achievement of carbon reduction.

### 2021-06-21 publications/2020-03-paper/revisions/cover-letter/cover_letter.tex
Adds 'track changes' copy

Please find enclosed our manuscript entitled: ``The role of current and emerging technologies in meeting Japan's mid- to long-term carbon reduction goals'' which I and my co-authors, Chapman, Minami, Stubbins, and Huff 
are submitting for exclusive consideration for publication as a research 
article in Applied Energy.

Our work uses the TIMES framework to explore decarbonisation pathways for the Japanese electricity supply sector using conventional and emerging (hydrogen, carbon capture and sequestration, and emerging photovoltaic cells) technologies. This work is novel in its inclusion of nascent technologies like solid oxide electrolysers and photochemical water splitting reactors, long-term impact evaluation up to the year 2100, life-cycle emissions for all technologies, and projections and learning curves for parameters like capital costs. We assess emerging technologies’ impact using a rigorous sensitivity analysis.

Our results approach true carbon-neutrality with the incorporation of lifecycle emissions. We also find that Japan can achieve energy security while mitigating emissions using renewable-based hydrogen. Further, incorporation of nuclear along with hydrogen emerges as an economically viable strategy. Our sensitivity analysis identifies key emerging technologies, and their most impactful parameters.

Our work offers a detailed comparative assessment of transition strategies to global energy analysts and Japanese policymakers. Our sensitivity analysis will also inform near-term deployment goals of mature technologies and long-term research objectives for lab-scale technologies in Japan.

@@

\closing{Sincere regards,\\
%\includegraphics[height=2cm]{signature}\\
\fromsig{Anshuman Chaube\\PhD Candidate\\Nuclear, Plasma, \& Radiological 
Eng.\\University of Illinois.\\achaube2@illinois.edu}
}

>>>>

Please find enclosed a revised version of our manuscript entitled: ``The role of current and emerging technologies in meeting Japan's mid- to long-term carbon reduction goals'' which I and my co-authors, Chapman, Minami, Stubbins, and Huff 
are submitting for exclusive consideration for publication as a research article in Applied Energy.

Thank you for giving us the opportunity to revise and resubmit our manuscript. The comments provided by the reviewers were considered seriously and their feedback has improved the readability and academic rigour of our work.

We look forward to working with you towards moving towards publication.

@@

\closing{Sincere regards,\\
%\includegraphics[height=2cm]{signature}\\
\fromsig{Anshuman Chaube\\PhD Candidate\\Nuclear, Plasma, \& Radiological 
Eng.\\University of Illinois at Urbana-Champaign.\\achaube2@illinois.edu}
}
